Modeling the near-wake of a vertical-axis cross-flow turbine with 2-D and 3-D RANS

### 2016-10-02 paper.tex
Explain how experimental measurements were taken

        \caption{Mean velocity field at $x/D=1$ from experiments
            \cite{Bachant2016-RVAT-Re-dep}.}

@@

        \caption{Turbulence kinetic energy at $x/D=1$ from experiments
            \cite{Bachant2016-RVAT-Re-dep}.}

>>>>

        \caption{Mean velocity field at $x/D=1$ from acoustic Doppler
        velocimetry measurements in a towing
        tank~\cite{Bachant2016-RVAT-Re-dep}.}

@@

        \caption{Turbulence kinetic energy at $x/D=1$ from acoustic Doppler
        velocimetry measurements in a towing
        tank~\cite{Bachant2016-RVAT-Re-dep}.}
